---
title: "Impacts of Social Media on Muslim Women"
subtitle: "A summary report on a research project <add more things here>"
format:
  lumo-html: 
    logo: "logo.png"                             # Optional. Path to a logo displayed above the title
    # github-repo: "https://www.github.com"        # Optional. Adds a github corner at the top right
    primary-color: "#1d2b70"
    self-contained: true
    is-particlejs-enabled: false                  # Optional: display interactive particles in the document header
author: NYM Ink
date: last-modified
---

## Introduction

Social media's harmful effects are particularly significant for women, including Muslim women. As of 2022, 4.6 billion people use social media globally, with women, especially those aged 18-29, being the heaviest users. Women also tend to spend more time on social media than men. 

Studies have shown negative impacts on body image and self-esteem, especially among younger women. However, there is limited research on the deeper psychospiritual effects of social media on Muslim women. 

This document aims to explore these effects and offer evidence-based solutions to mitigate them.


## Load Packages

Make sure to load **all your packages** at the start of your document for clarity and consistency.

Notice that the code chunks are folded by default. You can adjust this behavior with the `code-fold` option in the document's YAML header.


```{r, warning=F, message=F}
install.packages("paletteer", repos = "http://cran.us.r-project.org")

library(tidyverse) 
library(hrbrthemes) # <1>
library(paletteer) # <2>

```

1. this package provides my favorite `ggplot2` theme: `theme_ipsum()`

## Research Areas
We divided the research into several categories to analyze as we collected results. This was subject to change during the course of our research, but we finalized the following for our analysis.

### Misinformation of Islam

### Iman and Ibadah

### Ego and pride

### Negative mindset

### Impact of influencers

### Daily living and relationships

### Hijab and modesty

## Primary Research

### Results

### Discussion

## Session Info

When creating a Quarto document, it's a good practice to include details about your **working environment**. 

This is easy to do—just call `sessionInfo()`, and it will print out all your R and package versions. This simple step greatly enhances **reproducibility**.


<button type="button" data-bs-toggle="collapse" data-bs-target="#collapseOne" >Session Information</button><div id="collapseOne" class="accordion-collapse collapse"><div>


```{r}
sessionInfo()
```

</div></div>

## Possible Solutions

### Case study solution: Camp Sunnah

### Information sharing

### Time blocking method with a purpose


